---
title: "Data Exploration"
author: "Tom Peng"
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **USArrests** Dataset

The ``USArrests`` dataset is built-in to ``R`` and it has arrests per 100,000 residents for various crimes in the US states in 1973. For more details of the dataset, see the R Documentations page [here](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/USArrests.html)

To help us have a better understanding of what the dataset looks like, the ``head`` and ``tail`` commands lets us see the first and last six rows of the data, respectively:

```{r head}
head(USArrests)
```

```{r tail}
tail(USArrests)
```

``R`` has a built-in function ``summary`` which, as the function name suggests, shows us summary information on each column of the dataframe:

```{r USArrests}
summary(USArrests)
```

If we want to look at one column of the dataframe, we can use square brackets and the column name to extract it from the data:

```{r column_extract}
USArrests$Assault
```

We can also use ``R`` functions to find, for example, which state has the highest murder rate:

```{r highest_murder}
row.names(USArrests[which(USArrests["Murder"]==max(USArrests["Murder"])),])
```

## Visualization

We can plot the dataset to visualize the data. The `UrbanPop` column was removed from the plot so we can compare the different arrest rates.

```{r pressure, echo=FALSE}
plot(cbind(USArrests[1:2],USArrests[4]))
```

<!---Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.--->
